---
title: "Journal (reproducible report)"
author: "Pradnil S Kamble"
date: "2020-11-28"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Assingment 1

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

```{r}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----
# P1x

#libraries ----
library(tidyverse)
library(readxl)
library(lubridate)
library("writexl")

# Importing Files ----
bikes_tbl      <- read_excel("bikes.xlsx")
orderlines_tbl <- read_excel("orderlines.xlsx")
bikeshops_tbl <- read_excel("bikeshops.xlsx")

# Examining Data ----
View(orderlines_tbl)
View(bikeshops_tbl)
View(bikes_tbl)

# Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>% left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>% left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>% separate(col    = location, into   = c("city", "State"), sep    = ",") %>% 
mutate(total.price = price * quantity) %>% rename(bikeshop = name) %>% set_names(names(.) %>% str_replace_all("\\.", "_"))

# Business Insights ----

# Sales by State ----

# 1 - Manipulate
sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>% select(State, total_price) %>% group_by(State) %>% summarize(sales = sum(total_price)) %>%
mutate(sales_text = scales::dollar(sales, big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €"))
View(sales_by_state_tbl)

sales_by_city_tbl <- bike_orderlines_wrangled_tbl %>% select(city, total_price) %>% group_by(city) %>% summarize(sales = sum(total_price)) %>%
mutate(sales_text = scales::dollar(sales, big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €"))
View(sales_by_city_tbl)

# 2 - Visualize


sales_by_state_tbl %>%
ggplot(aes(x = State, y = sales)) +
geom_col(fill = "#2DC6D6") + 
geom_label(aes(label = sales_text)) +
geom_smooth(method = "lm", se = FALSE) + 
scale_y_continuous(labels = scales::dollar_format(big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €")) +
labs(title    = "Revenue by state", subtitle = "Upward Trend", x = "", y = "Revenue")+
theme(axis.text.x = element_text(angle = 45, hjust = 1))


sales_by_city_tbl %>%
ggplot(aes(x = city, y = sales)) +
geom_col(fill = "#2DC6D6") + 
geom_label(aes(label = sales_text)) +
geom_smooth(method = "lm", se = FALSE) + 
scale_y_continuous(labels = scales::dollar_format(big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €")) +
labs(title    = "Revenue by city", subtitle = "Upward Trend", x = "", y = "Revenue")+
theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Sales by Year and location ----

# 1 - Manipulate
sales_by_location_year_tbl <- bike_orderlines_wrangled_tbl %>% select(State, order_date, total_price) %>%  mutate(year = year(order_date)) %>%
group_by(State ,year) %>% summarize(sales = sum(total_price)) %>% mutate(sales_text = scales::dollar(sales, big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €"))
View(sales_by_location_year_tbl)

# 2 - Visualize
sales_by_location_year_tbl %>%
ggplot(aes(x = year, y = sales)) +
geom_col(fill = "#2DC6D6") + 
geom_label(aes(label = sales_text)) +
geom_smooth(method = "lm", se = FALSE) + 
scale_y_continuous(labels = scales::dollar_format(big.mark = ".", decimal.mark = ",", prefix = "", suffix = " €")) +
labs(title    = "Revenue by state and year", subtitle = "Upward Trend", x = "", y = "Revenue")+
theme(axis.text.x = element_text(angle = 45, hjust = 1))+
facet_wrap(vars(State))
```



# Assignment 2

```{r}
library(tidyverse) 
library(rvest)    
library(xopen)    
library(jsonlite) 
library(glue)     
library(stringi) 

url_home <- "https://www.radon-bikes.de/"
xopen(url_home) 

html_home <- read_html(url_home)
list_of_product_types <- html_home%>%
  html_nodes(css = ".megamenu__item > a")%>%
  html_text()


list_of_products_url <- html_home %>%
  html_nodes(".megamenu__item > a") %>%
  html_attr("href") %>%
  enframe(name = NULL, value = "url") %>%
  mutate(url = str_glue("https://www.radon-bikes.de{url}"))


bike_category_url <- list_of_products_url$url[1]

xopen(bike_category_url)


html_bike_category  <- read_html(bike_category_url)
temp_url <- html_bike_category%>%
  html_node(".a-button--hollow-secondary")%>%
  html_attr("href")%>%
  enframe(name = NULL, value = "url") %>%
  mutate(url = str_glue("https://www.radon-bikes.de{url}"))

temp_url <- temp_url$url[1]
xopen(temp_url)

bike_category_grid_html <- read_html(temp_url)

list_of_product_names <- bike_category_grid_html%>%
  html_nodes(css=".m-bikegrid__info > a > div > h4")%>%
  html_text%>%
  stringr::str_replace_all(pattern = "\n","")%>%
  stringr::str_replace_all(pattern = "  ","")%>%
  enframe(name = NULL, value = "NAME")



list_of_product_prices <- bike_category_grid_html%>%
  html_nodes(css=".m-bikegrid__price--active")%>%
  html_text()%>%
  stringr::str_extract(pattern = "[0-9€]+")%>%
  stringr::str_replace(pattern = "€","")%>%
  as.numeric()%>%
  enframe(name = NULL, value = "PRICE")

list_of_product_prices = na.omit(list_of_product_prices)
```

# Assignment 3

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.

# Assignment 4

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.

